---
title: "1st Assignment"
author: "José Monzón Egana"
date: "9/26/2021"
output:
  html_document: default
  word_document: default
  pdf_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(magrittr)
library(skimr)
```
```{r}
my_data <- read.csv2(file.choose())
#data <- read.csv('Final Assignment Data Analysis.csv', header = TRUE, sep=";")
```
```{r}
framaCPH <- my_data
```

```{r}
framaCPH %>% head()
```
```{r}
framaCPH %>% skim()
```

```{r}
framaCPH %>% summary()
```

```{r}
framaCPH %>% glimpse()
```
```{r}
framaCPH <- my_data[-c(22,23)]
```
Renaming columns that had a space between words
```{r}
framaCPH %<>%
rename(
    salestotal = Sales..Total..DKK.,
    date = Sales..Order.Date,
    folder= Product..Folder,
    pricelist = Order..Pricelist,
    market = Order..Market,
    collection = Product..Collection,
    sku = Product..Product.SKU,
    orderid = Sales..Order.ID,
    brand = Product..Brand,
    city = Billing.Invoice.Address..City,
    state = Billing.Invoice.Address..State,
    account_id = Account..Account.Number,
    IP = Order..IP,
    prod_name = Product..Product,
    units = Sales..Units,
    supplier = Product..Supplier,
    variant = Product..Variant,
    country = Country,
    account_name = Account..Account.Name
    )
```
```{r}
  framaCPH$date <- str_sub(framaCPH$date,1,nchar(framaCPH$date)-6)
  framaCPH$date <- as.Date(framaCPH$date, "%d/%m/%Y")
```

Random check
```{r}
framaCPH %>%
  count(country== 'Denmark')
```
mean, median, min & max value per nationality

```{r}
framaCPH %>%
  group_by(country) %>%
  filter(country != "Korea, Republic of") %>%
  summarize(orders= n(), total_sales = sum(salestotal), mean.salestotal = mean(salestotal, na.rm = TRUE), median.salestotal = median(salestotal, na.rm = TRUE), max.salestotal = max(salestotal, na.rm= TRUE)) %>%
  ungroup() %>%
  arrange(desc(orders)) %>%
  head(1)
```
grouped by account ID
```{r}
salesbycustomer <- framaCPH %>%
  group_by(market, country) %>%
  summarize(orders= n(), total_sales = sum(salestotal)) %>%
  filter(orders > 200) %>%
  ungroup() %>%
  arrange(desc(orders))
```

```{r}
#library(ggplot2)
ggplot(salesbycustomer, aes(x=country, y=total_sales )) + 
  geom_bar(stat = "identity")
# Calculate the future positions on the x axis of each bar (left border, central position, right border)

#ggplot(salesbycustomer, aes(x=country, fill=orders )) + 
 # geom_bar( ) +
  #scale_fill_hue(c = 40) +
  #theme(legend.position="none")
```

```{r}
framaCPH %>%
  group_by(state) %>%
  filter(str_detect(country, "United States")) %>%
  summarize(orders = n(), mean.salestotal = mean(salestotal, na.rm = TRUE), max.salestotal = max(salestotal, na.rm= TRUE)) %>%
  ungroup() %>%
  arrange(desc(orders))
```
```{r}
library(RColorBrewer)
marketgroup <- framaCPH %>%
  group_by(market) %>%
  summarise(salestotal = sum(salestotal)) %>%
  ungroup()
```


```{r}
coul <- brewer.pal(5, "Set2") 
barplot(height=marketgroup$salestotal, names=marketgroup$market, col=coul )
```
```{r}
framaCPH %>%
  filter(market == "Europe") %>%
ggplot(aes(x = salestotal, fill = country)) +
        ggtitle ("distribution of spending per orders ") +
  geom_histogram()
  scale_x_log10()
```
```{r}
framaCPH %>%
  filter(country == "Denmark") %>%
ggplot(aes(x = salestotal,fill = collection)) +
        ggtitle ("orders by collection ") +
  geom_histogram()
  scale_x_log10()
```
```{r}
framaCPH %>%
  filter(country == "United States") %>%
ggplot(aes(x = salestotal, fill = collection)) +
        ggtitle ("distribution of spending per orders ") +
  geom_histogram()
  scale_x_log10()
```
```{r}
framaCPH %>%
  filter(market == "Asia") %>%
ggplot(aes(x = salestotal, fill = country)) +
        ggtitle ("distribution of spending per orders ") +
  geom_histogram()
  scale_x_log10()
```

```{r}
test <- framaCPH %>% mutate(Year=format(as.Date(framaCPH$date), "%Y")) %>%
  group_by(country) %>% 
  summarise(orders = n(),salestotal = sum(salestotal), mean.Gross.Margin = mean(Gross.Margin, na.rm = TRUE))
```


```{r}
test %>% 
arrange(desc(mean.Gross.Margin))
 # select(country, aggregate(salestotal), Year)
 #head()
  #filter(country == "Denmark") %>%
   # ggplot(mapping=aes(x=Year, y=salestotal, col=market)) + geom_line()
```
```{r}
test1 <- framaCPH %>% mutate(Year=format(as.Date(framaCPH$date), "%Y")) %>%
  group_by(market) %>% 
    summarise(orders = n(),salestotal = sum(salestotal), mean.Gross.Margin = mean(Gross.Margin, na.rm = TRUE)) %>%
    filter(orders > 100)
test1 %>% 
arrange(desc(mean.Gross.Margin))
 # select(country, aggregate(salestotal), Year)
 #head()
  #filter(country == "Denmark") %>%
   # ggplot(mapping=aes(x=Year, y=salestotal, col=market)) + geom_line()
```
```{r}
install.packages('RColorBrewer')
library(RColorBrewer)
myPalette <- brewer.pal(6, "Set2") 
pct <- round(test1$salestotal/sum(test1$salestotal)*100)
lbls <- paste(test1$market, pct) # add percents to labels
lbls <- paste(lbls,"%",sep="") # ad % to labels
pie(test1$salestotal,labels = lbls, col=myPalette,
   main="Historical Relative importance of Market")
```
```{r}
sales_europe <- framaCPH %>% mutate(Year=format(as.Date(framaCPH$date), "%Y")) %>%
  filter(market == "Europe") %>%
  filter(country != "Denmark") %>%
  filter(salestotal > 5000) %>%
  group_by(country) %>% 
    summarise(orders = n(),salestotal = sum(salestotal), mean.Gross.Margin = mean(Gross.Margin, na.rm = TRUE)) %>%
      filter(orders > 20)
```
```{r}
pct3 <- round(sales_europe$salestotal/sum(sales_europe$salestotal)*100)
lbls3 <- paste(sales_europe$country, pct3) # add percents to labels
lbls3 <- paste(lbls3,"%",sep="") # ad % to labels
pie(sales_europe$salestotal,labels = lbls3, col=myPalette,
   main="Historical importance of Euro countries in the Euro Market (w/o DK)")
```

```{r}
sales_states <- framaCPH %>% mutate(Year=format(as.Date(framaCPH$date), "%Y")) %>%
  filter(country == "United States") %>%
  group_by(city) %>% 
    summarise(orders = n(),salestotal = sum(salestotal), mean.Gross.Margin = mean(Gross.Margin, na.rm = TRUE)) %>%
      filter(orders > 20)
```
```{r}
pct2 <- round(sales_states$salestotal/sum(sales_states$salestotal)*100)
lbls2 <- paste(sales_states$city, pct2) # add percents to labels
lbls2 <- paste(lbls2,"%",sep="") # ad % to labels
pie(sales_states$salestotal,labels = lbls2, col=myPalette,
   main="Historical Relative importance of Market")
```
Network Analysis
I will analyze the network of Frama's customers in the US during 2021.
For that I will filter the data and then convert some of the categorical variables such as collections, brands or folders to integers, so I can create the association between nodes.
```{r}
framanw <- framaCPH %>% 
  filter(country == 'United States') %>%
  filter(date >= as.Date("2021-01-01")) %>%
  arrange(date)
```
```{r}
framanw
```


```{r}
framanw$brand.r <- as.integer(as.factor(framanw$brand))
framanw$collection.r <- as.integer(as.factor(framanw$collection))
framanw$folder.r <- as.integer(as.factor(framanw$folder))
```
```{r}
framanw %>% count(account_id, sort = TRUE)
```
In this step I will create the connection between the customers and the collections.
The result will be the customers that share interest in the same collections
```{r}
el_2m <- framanw %>%
  select(account_id, collection.r) 
el <- el_2m %>%
  left_join(el_2m %>% select(account_id, collection.r), by = "collection.r") 
el %<>% 
  select(-collection.r) %>%
  rename(from = account_id.x, 
         to = account_id.y) %>%
  filter(from != to)
el %<>%
  count(from, to, name = 'weight')  %>%
  mutate(weight = (weight) )
el %>% 
  arrange(desc(weight)) %>%
  head()
```
This graph shows the distribution of the connection between customers.
As can be seen, most of the customers have a pretty low affiliation, while some of them can reach up to 70.
```{r}
el %>% 
  ggplot(aes(x = weight)) +
  geom_histogram()
```
I will filter out the weight affiliation smaller than 5 because I want to create a network of good customers.
```{r}
el %>% 
  filter(weight > 4) %>%
  filter(weight < 40) %>%
    ggplot(aes(x = weight)) +
  geom_histogram()
```
```{r}
nodes <- framanw %>%
  distinct(account_id, .keep_all = TRUE) %>%
  select(account_id, account_name, collection, collection.r) %>%
  rename(person_name = account_name,
         name = account_id) %>%
  mutate(name = name %>% as.character())
```
```{r}
library(ggplot2)
library(igraph)

  g <- el %>% as_tbl_graph(directed = FALSE) %>%
  igraph::simplify() %>%
  as_tbl_graph(directed = FALSE)
```
```{r}
g <- g %N>% 
filter(!node_is_isolated()) %N>% 
  filter(percent_rank(centrality_degree(weights = weight)) >= 0.5)
```

```{r}
g <- g %N>%
  mutate(community = group_louvain(weights = weight) ) 
```
```{r}
g <- g %N>%
  morph(to_split, community) %>% 
    mutate(cent_dgr_int = centrality_degree(weights = weight)) %>%
    mutate(com_center = cent_dgr_int == max(cent_dgr_int)) %>%
  unmorph()
```

```{r}
g %N>%
  as_tibble() %>%
  count(community)
```

```{r}
g <- g %N>%
  left_join(nodes, by = c('name' = 'name'))

#left_join(data %>% select(EID, title, journal, year, citations), by = c('name' = 'EID')) %>%
 # mutate(title = title %>% str_trunc(30))
```


```{r}
g %>%
  ggraph(layout = 'graphopt') + 
  geom_edge_link(aes(width = weight,
                     color = .N()$community[from] %>% as.factor()),
                alpha = 0.5, 
                show.legend = FALSE) +
      scale_edge_width(range = c(0.1, 2)) + 
  geom_node_point(aes(color = community %>% as.factor(),
                      size = centrality_degree(weight = weight), 
                      )) +
  geom_node_text(aes(label = person_name, filter = com_center == TRUE), repel = TRUE) +
  theme_graph()   + 
  theme(legend.position = 'bottom') + 
  labs(title = 'Network of US recurring customers',
       subtitle = 'as of 2021 YTD',
       color = 'Community',
       size = 'Degree')
```

```{r}
framanw2 <- framaCPH %>% 
  filter(country == 'Spain') %>%
  filter(date >= as.Date("2021-01-01")) %>%
  arrange(date)
```
```{r}
framanw2
```

```{r}
framanw2$collection.r <- as.integer(as.factor(framanw2$collection))
```
```{r}
framanw2 %>% count(account_id, sort = TRUE)
```
In this step I will create the connection between the customers and the collections.
The result will be the customers that share interest in the same collections
```{r}
el_2msp <- framanw2 %>%
  select(account_id, collection.r) 
elsp <- el_2msp %>%
  left_join(el_2m2 %>% select(account_id, collection.r), by = "collection.r") 
elsp %<>% 
  select(-collection.r) %>%
  rename(from = account_id.x, 
         to = account_id.y) %>%
  filter(from != to)
elsp %<>%
  count(from, to, name = 'weight')  %>%
  mutate(weight = (weight) )
elsp %>% 
  arrange(desc(weight)) %>%
  head()
```
This graph shows the distribution of the connection between customers.
As can be seen, most of the customers have a pretty low affiliation, while some of them can reach up to 35.
```{r}
elsp %>% 
  ggplot(aes(x = weight)) +
  geom_histogram()
```
I will filter out the weight affiliation smaller than 2 because I want to create a network of recurring customers. However, since they are less than their US counterparts, I will just filter out customers who only bought once.
```{r}
elsp %>% 
  filter(weight > 2) %>%
    ggplot(aes(x = weight)) +
  geom_histogram()
```
```{r}
nodessp <- framanw2 %>%
  distinct(account_id, .keep_all = TRUE) %>%
  select(account_id, account_name, collection, collection.r) %>%
  rename(person_name = account_name,
         name = account_id) %>%
  mutate(name = name %>% as.character())
```
```{r}
gsp <- elsp %>% as_tbl_graph(directed = FALSE) %>%
  igraph::simplify() %>%
  as_tbl_graph(directed = FALSE)
```
```{r}
gsp <- gsp %N>% 
filter(!node_is_isolated()) %N>% 
  filter(percent_rank(centrality_degree(weights = weight)) >= 0.1)
```

```{r}
gsp <- gsp %N>%
  mutate(community = group_louvain(weights = weight) ) 
```
```{r}
gsp <- gsp %N>%
  morph(to_split, community) %>% 
    mutate(cent_dgr_int = centrality_degree(weights = weight)) %>%
    mutate(com_center = cent_dgr_int == max(cent_dgr_int)) %>%
  unmorph()
```

```{r}
gsp %N>%
  as_tibble() %>%
  count(community)
```

```{r}
gsp <- gsp %N>%
  left_join(nodessp, by = c('name' = 'name'))

#left_join(data %>% select(EID, title, journal, year, citations), by = c('name' = 'EID')) %>%
 # mutate(title = title %>% str_trunc(30))
```


```{r}
gsp %>%
  ggraph(layout = 'graphopt') + 
  geom_edge_link(aes(width = weight,
                     color = .N()$community[from] %>% as.factor()),
                alpha = 0.5, 
                show.legend = FALSE) +
      scale_edge_width(range = c(0.1, 2)) + 
  geom_node_point(aes(color = community %>% as.factor(),
                      size = centrality_degree(weight = weight), 
                      )) +
  geom_node_text(aes(label = person_name, filter = com_center == TRUE ), repel = TRUE) +
  theme_graph()   + 
  theme(legend.position = 'bottom') + 
  labs(title = 'Network of Spanish customers',
       subtitle = 'as of 2021 YTD',
       color = 'Community',
       size = 'Degree')
```